Neuro V

### 2017-09-07 neuro5.rmd
completing week 9

-  Electromyography: may show changes of chronic partial denervation, ab~N spontaneous activity in resting muscle. Dx should not be made with confidence unless change are found in $\geq3# spinal regions, or $2$ regions + bulbar 
-  Motor conduction velocity is usually normal
-  Sensory conduction studies normal
-  Biopsy of wasted muscle
-  Serum CK may be elevated, but not as high as muscular dystrophies
-  CSF normal

@@

>>>>

-  Electromyography: may show changes of chronic partial denervation, ab~N spontaneous activity in resting muscle. Dx should not be made with confidence unless change are found in $\geq3$ spinal regions, or $2$ regions + bulbar 
-  Motor conduction velocity is usually normal
-  Sensory conduction studies normal
-  Biopsy of wasted muscle
-  Serum CK may be elevated, but not as high as muscular dystrophies
-  CSF normal

@@

Proceed with consultation: direct Q at pt, ask to have a chat with husband

Dx: can get advanced health directive, clin trials, gives pt time to do stuff before dying, interventions can help

Depression, dementia, delirium have to d/dx

Commonest causes of memory impairment: important to know ddx as some are treatable

-  Dementia
-  Alzheimers
-  Parkinsons
-  Thyroid
-  Depression
-  Cerebral infn
-  Sleep deficiencies

Classification of dementia: 4 main types = {alzheimers, lewy body (concentration, distances, *visual hallucinations, parkinsonism, fluctuation in mental state*), vascular (step deterioration, sudden onset), frontotemporal}

Specific cognitive tests:

-  MMSE: out of 30, few questions testing working, visualspacial awareness,... Below 28 get concerned. This is biased
-  GPCOG: piece of paper for both pt and their SO

Ex and Ix: to mainly rule stuff out

-  Bloods + Vit B12
-  LP
-  Prions
-  MRI
-  PET

Aged care assessment, talk to both people at once, discuss prognosis, mental exercises

Medications: cholinesterase inhibitors, NMDA-R antagonists, symptomatic stuff for sleeping, craziness, antidepressants
